Background of This Project

### 2019-11-15 NB_v4_new_data.Rmd
update

A truth table lists how many of the predicted categories are in their correct categories. Adding diagonally and dividing by total count gives the percent accuracy at predicting Subject. 
```{r}
# Create a truth table by tabulating the predicted class labels with the actual class labels 
table("Predictions"= comments_test_pred_subject,  "Actual Subject Test" = comments_test_labels_subject )
table("Predictions"= comments_all_pred_subject,  "Actual Subject All" = comments_all_labels_subject )
table("Predictions"= comments_test_pred_structure,  "Actual Structure Test" = comments_test_labels_structure )
table("Predictions"= comments_all_pred_structure,  "Actual Structure All" = comments_all_labels_structure )

@@

The faster method is to calculate a confusion matrix, which displays BOTH the truth table, and the final overall accuracy. A confusion matrix can be queried for specific values.
```{r reportOut}
# Prepare the confusion matrix. 
conf.mat1 <- confusionMatrix(comments_test_pred_subject, comments_test_labels_subject)
conf.mat2 <- confusionMatrix(comments_all_pred_subject, comments_all_labels_subject)
conf.mat3 <- confusionMatrix(comments_test_pred_structure, comments_test_labels_structure)
conf.mat4 <- confusionMatrix(comments_all_pred_structure, comments_all_labels_structure)

@@

# This block outputs both the overall and by-group accuracy values for Structure x Test Subset.
print ("Test, Structure")
conf.mat3

# This block outputs by-group accuracy values in a single column for Structure x Test Subset. 
print ("Test, Structure")
conf.mat3$byClass

# This block outputs a single line table with overall accuracy, kappa, lower and higher limits of accuracy, accuracy null value, P value for accuracy, and Mcnemar P value for Structure x Test Subset.
print ("Test, Structure")
conf.mat3$overall

# This block outputs JUST the overall accuracy value for Structure x Test Subset. 
conf.mat3$overall['Accuracy']
print ("Test, Structure")

# This block outputs both the overall and by-group accuracy values for Structure x All Data.
print ("All, Structure")
conf.mat4

# This block outputs by-group accuracy values in a single column for Structure x All Data. 
print ("All, Structure")
conf.mat4$byClass

# This block outputs a single line table with overall accuracy, kappa, lower and higher limits of accuracy, accuracy null value, P value for accuracy, and Mcnemar P value for Structure x All Data.
print ("All, Structure")
conf.mat4$overall

# This block outputs JUST the overall accuracy value for Structure x All Data. 
print ("All, Structure")
conf.mat4$overall['Accuracy']
```

>>>>

A truth table lists how many of the predicted categories are in their correct categories. Adding diagonally and dividing by total count gives the percent accuracy at predicting Subject. 
```{r}
# Create a truth table by tabulating the predicted class labels with the actual class labels 
table("Predictions"= comments_test_pred_subject,  "Actual Subject Test" = comments_test_labels_subject )
table("Predictions"= comments_all_pred_subject,  "Actual Subject All" = comments_all_labels_subject )
#table("Predictions"= comments_test_pred_structure,  "Actual Structure Test" = comments_test_labels_structure )
#table("Predictions"= comments_all_pred_structure,  "Actual Structure All" = comments_all_labels_structure )

@@

The faster method is to calculate a confusion matrix, which displays BOTH the truth table, and the final overall accuracy. A confusion matrix can be queried for specific values.
```{r reportOut}
# Prepare the confusion matrix. 
conf.mat1 <- confusionMatrix(comments_test_pred_subject, comments_test_labels_subject)
conf.mat2 <- confusionMatrix(comments_all_pred_subject, comments_all_labels_subject)
#conf.mat3 <- confusionMatrix(comments_test_pred_structure, comments_test_labels_structure)
#conf.mat4 <- confusionMatrix(comments_all_pred_structure, comments_all_labels_structure)

@@

# This block outputs both the overall and by-group accuracy values for Structure x Test Subset.
#print ("Test, Structure")
#conf.mat3

# This block outputs by-group accuracy values in a single column for Structure x Test Subset. 
#print ("Test, Structure")
#conf.mat3$byClass

# This block outputs a single line table with overall accuracy, kappa, lower and higher limits of accuracy, accuracy null value, P value for accuracy, and Mcnemar P value for Structure x Test Subset.
#print ("Test, Structure")
#conf.mat3$overall

# This block outputs JUST the overall accuracy value for Structure x Test Subset. 
#conf.mat3$overall['Accuracy']
#print ("Test, Structure")

# This block outputs both the overall and by-group accuracy values for Structure x All Data.
#print ("All, Structure")
#conf.mat4

# This block outputs by-group accuracy values in a single column for Structure x All Data. 
#print ("All, Structure")
#conf.mat4$byClass

# This block outputs a single line table with overall accuracy, kappa, lower and higher limits of accuracy, accuracy null value, P value for accuracy, and Mcnemar P value for Structure x All Data.
#print ("All, Structure")
#conf.mat4$overall

# This block outputs JUST the overall accuracy value for Structure x All Data. 
#print ("All, Structure")
#conf.mat4$overall['Accuracy']
```

### 2019-11-15 background.Rmd
update

Undergraduate introductory STEM courses often include technical writing training. Often it is secondary to content coverage, and so treated as an incidental skill that each student develops "along the way." Alternatively, the writing instruction process may be haphazardly designed, implemented, and executed. Adding to the learning challenge, faculty may not be who is helping students develop writing skills. Often graduate teaching assistants or even advanced undergraduates are who teaches technical writing. TAs may have under-developed writing skills themselves, lack pedagogical content knowledge needed to guide students effectively, or not have been explicitly trained to teach writing in a particular way.

>>>>

Undergraduate introductory STEM courses often include technical writing training. Often it is secondary to content coverage, and treated as an incidental skill that each student develops "along the way." Alternatively, the writing instruction process may be haphazardly designed, implemented, and executed. Adding to the learning challenge, faculty may not be who is helping students develop writing skills. Often graduate teaching assistants or even advanced undergraduates are who teaches technical writing. TAs may have under-developed writing skills themselves, lack pedagogical content knowledge needed to guide students effectively, or not have been explicitly trained to teach writing in a particular way.
